% ═════════════════════════════════════════════════════════════════════════════
\section{Methodology}
\label{sec:methodology}

\subsection{Hypotheses}

Three testable hypotheses are derived from the literature:

\begin{description}
  \item[H1] CS2 skin index returns are significantly correlated with Bitcoin
    returns (market integration hypothesis).

  \item[H2] Bitcoin Granger-causes CS2 skin prices, but not vice versa ---
    motivated by the shared speculative, crypto-adjacent user demographic.

  \item[H3] CS2 exhibits higher volatility than the S\&P 500 but similar
    volatility clustering patterns to Bitcoin.
\end{description}

\subsection{Data}

CS2 skin transaction data are sourced from a publicly available Kaggle dataset
(CC-BY-NC-SA 4.0) containing Steam Marketplace records for 22,446 item
variants (10,833 distinct base items) spanning August 2013 to June 2024. The
sample is restricted to wearable item categories (weapon skins, knives, gloves)
and StatTrak variants are excluded. A liquidity filter drops any item recording
fewer than two transactions in any calendar month
\cite{six2024indexcriteria}, reducing the sample to 1,607 liquid base items.
The daily CS2 index level is:

\begin{equation}
  I_t = \frac{\sum_{i} p_{it} \cdot v_{it}}{\sum_{i} v_{it}}
  \label{eq:index}
\end{equation}

where $p_{it}$ is the item-level volume-weighted average price across wear
conditions on day $t$ and $v_{it}$ is the corresponding total daily trading
volume. This value-weighted aggregation mirrors market-capitalisation weighting
in equity indices \cite{msci2024indexconstruction}, ensuring that heavily traded
skins drive the index level. The index spans 3,960 trading days. Daily log
returns for the S\&P~500 (\texttt{\^{}GSPC}), Bitcoin (\texttt{BTC-USD}), and
Gold (\texttt{GC=F}) are retrieved via \texttt{quantmod}. The four series are
aligned via inner join on common trading days, yielding 2,448 observations
(September 2014 to June 2024) used in all multivariate analyses.

\subsection{Analytical Pipeline}

Exploratory data analysis covers descriptive statistics, a contemporaneous
Pearson correlation matrix (H1), and Augmented Dickey-Fuller tests with BIC
lag selection and a constant term to confirm stationarity of log returns. A
GARCH(1,1) model with student-$t$ innovations is then fitted to each return
series to compare unconditional volatility and shock persistence across assets
(H3). Finally, a VAR($p$) model is estimated on the joint system with the lag
order selected by BIC; Granger causality is tested via F-tests on jointly
excluded lag coefficients in both directions between each benchmark and CS2
(H2).
