% ═════════════════════════════════════════════════════════════════════════════
\section{Conclusion}
\label{sec:conclusion}

This paper investigated whether the CS2 skin market is integrated with
traditional and crypto financial markets. Using a daily value-weighted price
index from 1,607 liquid skins over the period August 2013 to June 2024, we
tested for integration against the S\&P~500, Bitcoin, and Gold via EDA,
GARCH(1,1), and a VAR(4) with Granger causality tests.

\textbf{The evidence consistently points to a lack of integration: the CS2 skin
market is not integrated with any of the three comparison assets.}
Contemporaneous correlations are indistinguishable from zero and no Granger
causal relationship is detected at the 5\% significance level in either
direction. H1 and H2 are rejected; H3 is partially supported --- CS2 shares
Bitcoin's total volatility persistence ($\hat{\alpha}+\hat{\beta}=0.9990$)
but differs markedly in shock reactivity, with CS2 exhibiting regime-like
plateaus rather than Bitcoin's spike-and-decay pattern. The near-zero
correlation with all mainstream assets confers meaningful diversification
potential for investors already holding equity or crypto positions, corroborating
the low-correlation finding of \citeauthor{dobrynskaya2025videogame}
\cite{dobrynskaya2025videogame}. However, CS2 skins function as an idiosyncratic
zero-beta diversifier rather than a systematic hedge: their value lies in low
correlation with other markets, not in negative co-movement. Extreme annualised
volatility (114.56\%) and the absence of price-discovery linkages to broader
markets further limit their practical appeal for risk-averse investors.

The main limitations are the restriction to Steam Marketplace data (excluding
third-party platforms such as Skinport or CS.Money), the value-weighting bias
towards liquid skins, and the potential structural break at the CS:GO-to-CS2
engine transition in September 2023. Future work should test for this breakpoint
explicitly, estimate a pairwise CS2--Bitcoin VAR as a robustness check, and
incorporate data from third-party platforms and equal-weighted benchmarks to
obtain a more complete picture of CS2 skin price dynamics.
