% ═════════════════════════════════════════════════════════════════════════════
\section*{List of Abbreviations}
\addcontentsline{toc}{section}{List of Abbreviations}
\label{sec:abbreviations}

\begin{tabular}{p{3.5cm} p{10cm}}
  \textbf{ACF}   & Autocorrelation Function \\[4pt]
  \textbf{ADF}   & Augmented Dickey-Fuller (unit root test) \\[4pt]
  \textbf{AIC}   & Akaike Information Criterion \\[4pt]
  \textbf{BIC}   & Bayesian Information Criterion (Schwarz Criterion, SC) \\[4pt]
  \textbf{CS2}   & Counter-Strike 2 \\[4pt]
  \textbf{FPE}   & Final Prediction Error \\[4pt]
  \textbf{GARCH} & Generalised Autoregressive Conditional Heteroskedasticity \\[4pt]
  \textbf{HQ}    & Hannan-Quinn Information Criterion \\[4pt]
  \textbf{PACF}  & Partial Autocorrelation Function \\[4pt]
  \textbf{VAR}   & Vector Autoregression \\[4pt]
  \textbf{VWAP}  & Volume-Weighted Average Price \\[4pt]
\end{tabular}

\bigskip

\section*{Glossary}
\addcontentsline{toc}{section}{Glossary}
\label{sec:glossary}

\begin{description}
  \item[CS2 (Counter-Strike 2)]
    Valve's tactical first-person shooter and the successor to Counter-Strike:
    Global Offensive (CS:GO). Launched in 2023, it operates the same Steam
    Marketplace ecosystem established in 2013, through which cosmetic items are
    traded at real-money prices.

  \item[Skin]
    A purely cosmetic weapon or equipment modification in CS2 with no gameplay
    effect. Skins are bought, sold, and stored as digital assets on the Steam
    Marketplace and constitute the asset class studied in this paper.

  \item[StatTrak]
    A skin variant equipped with an electronic counter that tracks the number
    of in-game kills. StatTrak skins command a persistent price premium
    relative to their non-StatTrak counterparts and are excluded from the index
    to avoid confounding price signals unrelated to market-wide demand.

  \item[Steam Marketplace]
    Valve Corporation's open secondary market integrated into the Steam gaming
    platform, through which users buy and sell in-game items at prices set by
    supply and demand. Unlike closed in-game economies, the Steam Marketplace
    allows freely negotiated prices denominated in real currency, making it
    amenable to standard financial time series analysis.

  \item[Value-weighted index]
    A price index in which each constituent's contribution to the index level
    is proportional to its trading volume. Formally, $I_t =
    \sum_i p_{it} v_{it} / \sum_i v_{it}$, where $p_{it}$ is the
    volume-weighted average price of item $i$ on day $t$ and $v_{it}$ is its
    trading volume. Analogous to market-capitalisation weighting in equity
    indices, this ensures that heavily traded items drive the index level.

  \item[Log return]
    The continuously compounded return defined as $r_t = \ln(P_t / P_{t-1})$.
    Preferred over simple returns because log returns are approximately
    additive over time, yield a stationary series when prices are
    non-stationary, and are symmetric around zero for up and down moves of
    equal magnitude.

  \item[Granger causality]
    A statistical concept introduced by \citeauthor{granger1969causal}
    \cite{granger1969causal}: variable $X$ Granger-causes $Y$ if past values of
    $X$ improve forecasts of $Y$ beyond what is achievable using $Y$'s own
    history alone. Granger causality is a statement about predictability, not
    structural or physical causation.

  \item[Liquidity filter]
    A selection criterion that excludes assets with insufficient trading
    activity from an index. In this paper, any base item recording fewer than
    two transactions in any calendar month is excluded, analogous to the SIX
    Swiss Exchange minimum turnover requirement for equity index inclusion
    \cite{six2024indexcriteria}.

  \item[Persistence ($\hat{\alpha} + \hat{\beta}$)]
    In a GARCH(1,1) model, the sum of the ARCH coefficient $\hat{\alpha}$ and
    the GARCH coefficient $\hat{\beta}$. Values close to unity indicate slow
    mean-reversion of conditional variance: a volatility shock today affects
    expected variance far into the future. A value of exactly 1 defines an
    integrated GARCH (IGARCH) process.
\end{description}
